---
title: "Real Data"
author: "248STG01 김다빈"
date: "`r Sys.Date()`"
output: html_document
---

# Real Data : epilepsy

# data frame with 236 observations of the following 7 variables.
# y :The seizure counts during 2-week periods before each of four visits #     to the clinic.
# T : Treatment(0=new drug, 1=placebo).
# B : The average number of epileptic seizures 
#    in the 8-week period preceding the trial 
# A  : The logarithm of age (in years) of each patient. 
# V :  Linear trend coded (-3,-1, 1, 3)/10 for four visits of each patient
# patient : Patient number for 59 epileptics.
# id : Observation number for 236 observations




# 데이터 불러오기

```{r}
library(dhglm)
data("epilepsy")
epilepsy


# Age
#exp(epilepsy$A)

#Base
#exp(epilepsy$B)*4

N = 236
t = 59
n = 4
p = 4000 #including 3994 noise covariates

```


# noise predictors 추가 및 standardized


```{r}
set.seed(12345)

#noise covariates generate
U <-  matrix(runif(N*3994,min = -1, max = 1),nrow = N)
colnames(U) <- paste0("U",1:3994)
```


```{r}
data <- data.frame(epilepsy, U)
head(data)
dim(data)

#id columns drop
data <- data[,-7]

#TRT 칼럼명 변경 
colnames(data)[2] <- 'trt'


data$patient <- as.factor(data$patient)  # 범주형으로 변환
data$trt <- as.factor(data$trt)

```


# V4 생성 

```{r}

data['V4'] <- 0
for(i in seq(1,59)){
  if( data[i*4,'y'] == 0) {
      data$V4[(i*4-3):(i*4)] <- 0 
      } 
  
  else {data$V4[(i*4-3):(i*4)] <- 1}
}

```


```{r}
# Standardized
#data <- data[,-5]
std_col <- c(1,2,6) 
data[,-std_col] <- as.data.frame(scale(data[,-std_col]))
```


```{r}
library(glmmLasso)


U_vars <- paste("U", 1:3394, sep = "")
U_vars <- paste(U_vars,collapse = " + ")
X_vars <- c("+ B" ,"A","B:A", "V","trt")
X_vars <- paste(X_vars,collapse = " + ")
form <- as.formula(paste("y ~ ",paste(U_vars,X_vars)))

# CV 
library(glmmLasso)
random_matrix <- model.matrix(~ patient - 1, data = data)
model <- glmmLasso(form, rnd = random_matrix, family = poisson(), lambda = 600, data = data)
model$coefficients[3390:3400]
model$bic  #300 이상이어야 돌아감
model$StdDev

sum(model$coefficients != 0)
```


#find best lambda

```{r}
lambdas <- seq(600,1750,by = 10)
result <- matrix(NA, nrow = length(lambdas), ncol = 2)
colnames(result) <- c('lambda','BIC')

for (i in 1:length(lambdas)) {
  random_matrix <- model.matrix(~ patient - 1, data = data)
  model <- glmmLasso(form, rnd = random_matrix, family =       poisson(), lambda = lambdas[i], data = data)
  result[i,] <- c(lambdas[i], model$bic)
}

print(result[which.min(result[,2]),])
```

```{r}


data['id'] <- epilepsy['id']
U_vars <- paste("U", 1:3394, sep = "")
U_vars <- paste(U_vars,collapse = " + ")
X_vars <- c("+ B" ,"A","B:A", "V","trt")
X_vars <- paste(X_vars,collapse = " + ")
form <- as.formula(paste("y ~ ",paste(U_vars,X_vars)))
random_matrix <- model.matrix(~ patient + id - 1, data = data)
model_test <- glmmLasso(form, rnd = random_matrix,
                       family = poisson(),
                       lambda = 1650,
                       data = data)
```


```{r}
#final model




model_fin <- glmmLasso(form, rnd = random_matrix,
                       family = poisson(),
                       lambda = 1650,
                       data = data)
model_fin$coefficients[3390:3400]
model_fin$bic  #300 이상이어야 돌아감
model_fin$StdDev

sum(model_fin$coefficients != 0)
```




# lambda plot

```{r}

library(ggplot2)
ggplot(aes(lambda, BIC), data = result) + 
  geom_line()
plot(result$lambda,result$BIC, type ='l')
```



```{r}

df <- epilepsy
epilepsy$patient <- as.factor(epilepsy$patient)
random_matrix <- model.matrix(~ patient - 1, data = epilepsy)
model <- glmmLasso(fix = y~B+A,rnd =random_matrix, family = poisson(link = log), lambda = 2, data= epilepsy)


```


# glmm

```{r}

library(lme4)
model <- glmer(y ~ B + A + B:A + V + trt + (1 | patient), family = poisson(link = log), data = data)

summary(model)
```






